### 2020-02-09 submission/methods.tex
clean up for submission

The  $\lambda_{i}$ is the $i^{th}$ eigenvalue of the $\mathbf{X}$, 
and $\lambda_{max}$ is the maximum eigenvalue.
Note the squared singular values $\sigma_{i}$ of $\mathbf{W}$, $\lambda_{i}=\sigma^{2}_{i}$.)
Also, note we do \emph{not} normalize $\mathbf{X}$ by $1/N$; see the Appendix for a discussion why.

>>>>

The  $\lambda_{i}$ is the $i^{th}$ eigenvalue of the $\mathbf{X}$, 
and $\lambda_{max}$ is the maximum eigenvalue.
Note, the eigenvalues are square of the singular values $\sigma_{i}$ of $\mathbf{W}$: $\lambda_{i}=\sigma^{2}_{i}$.
Also, note that we do \emph{not} normalize $\mathbf{X}$ by $1/N$; see the Appendix for a discussion why.
